---
title: "Project-Russian Federation"
author: "Julia Cuellar"
date: '2021-7-25'
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## EDA
```{r eval = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
library(latexpdf)
library(tinytex)
library(data.table)
library(tidyverse)
library(rjson)
library(readxl)
library(dplyr)
library(RSQLite)
setwd("C:/Users/jcuel/Videos/Bellevue/Summer 2021/Professor Williams/Projects/Project 2")
baikal_df = fread("Paleoclimatology - Baikal.txt", fill = TRUE)
lake_df = fromJSON(file = "Paleoclimatology - Lake.json")
lake2_df = read_excel("Paleoclimatology - Lake2.xls")
```

**Baikal Data:**
```{r eval = TRUE, echo = FALSE}
head(baikal_df)
```

**Summary of Baikal Data:**
```{r eval = TRUE, echo = FALSE}
summary(baikal_df)
```

**Display nulls of Baikal Data:**
```{r eval = TRUE, echo = FALSE}
is.null(baikal_df)
```

**Display NA's of Baikal Data:**
```{r eval = TRUE, echo = FALSE}
sum(is.na(baikal_df$Hole))
sum(is.na(baikal_df$`Core-Sec.-Int.`))
sum(is.na(baikal_df$Depth))
sum(is.na(baikal_df$Bio.sil.))
sum(is.na(baikal_df$Age))
sum(is.na(baikal_df$V6))
sum(is.na(baikal_df$V7))
```

**Rename columns of Baikal Data:**
```{r eval = TRUE, echo = FALSE}
colnames(baikal_df) = c("Hole", "Core-Sec", "Int", "Depth", "Biosil", "Age", "X")
colnames(baikal_df)
```

**Redisplay NA's of X:**
```{r eval = TRUE, echo = FALSE}
baikal_df = replace_na(baikal_df, list(`X` = mean(baikal_df$'X', na.rm = TRUE)))
sum(is.na(baikal_df$X))
```

**Redisplay Baikal Data:**
```{r eval = TRUE, echo = FALSE}
write.csv(baikal_df, "Paleoclimatology - Baikal.csv", row.names = FALSE)
head(baikal_df)
```

**Project Age column plot from Baikal data:**

```{r eval = TRUE, echo = FALSE}
boxplot(baikal_df$Age, main = 'Age of Baikal', xlab = 'age', col = 'bisque1', border = "cornsilk4", horizontal = TRUE, notch = TRUE)
```

**Lake Data:**
```{r eval = TRUE, echo = FALSE}
lake_df = read.delim("Paleoclimatology - Lake.txt", header = TRUE, sep = "\t", dec = ".")
colnames(lake_df) = c("Age-ka", "MTWM-degC", "MTWM-deg-C", "MTWM-deg+C", "PANN-mm", "PANN--mm", "PANN-+mm", "Trees & Shrubs", "Picea")
head(lake_df)
```

**Summary of Lake Data:**
```{r eval = TRUE, echo = FALSE}
summary(lake_df)
```

**Display nulls of Lake Data:**
```{r eval = TRUE, echo = FALSE}
is.null(lake_df)
```

**Display NA's of Lake Data:**
```{r eval = TRUE, echo = FALSE}
sum(is.na(lake_df))
```

**Rename Age-ka column to Age of Lake Data:**
```{r eval = TRUE, echo = FALSE}
names(lake_df)[1] = "Age"
colnames(lake_df)
```

**Redisplay Lake Data:**
```{r eval = TRUE, echo = FALSE}
write.csv(lake_df, "Paleoclimatology - Lake.csv", row.names = FALSE)
head(lake_df)
```

**Project Age column plot from Lake data:**

```{r eval = TRUE, echo = FALSE}
boxplot(lake_df$Age, main = 'Age of Lake', xlab = 'age', col = 'burlywood1')
```

**Lake 2 Data:**
```{r eval = TRUE, echo = FALSE}
head(lake2_df)
```

**Summary of Lake 2 Data:**
```{r eval = TRUE, echo = FALSE}
summary(lake2_df)
```

**Display nulls of Lake 2 Data:**
```{r eval = TRUE, echo = FALSE}
is.null(lake2_df)
```

**Display NA's of Lake 2 Data:**
```{r eval = TRUE, echo = FALSE}
sum(is.na(lake2_df))
```

**Rename Age-ka-BP column to Age of Lake 2 Data:**
```{r eval = TRUE, echo = FALSE}
names(lake2_df)[1] = "Age"
colnames(lake2_df)
```

**Change Lake 2 Data into Dataframe:**
```{r eval = TRUE, echo = FALSE}
lake2_df = data.frame(lake2_df)
lake2_df
```

**Redisplay Lake 2 Data:**
```{r eval = TRUE, echo = FALSE}
write.csv(lake2_df, "Paleoclimatology - Lake2.csv", row.names = FALSE)
head(lake2_df)
```

**Project Age column plot from Lake 2 data:**

```{r eval = TRUE, echo = FALSE}
boxplot(lake2_df$Age, main = 'Age of Lake 2', xlab = 'age', col = 'goldenrod1')
```

## Merge all file formats into a database
```{r eval = TRUE, echo = FALSE}
baikal = read.csv("Paleoclimatology - Baikal.csv")
lake = read.csv("Paleoclimatology - Lake.csv")
lake2 = read.csv("Paleoclimatology - Lake2.csv")
db = merge(lake, lake2, by = "Age", all = TRUE)
db_final = full_join(db, baikal, by = "Age", all = TRUE)
write.csv(db_final, "Paleoclimatology - Russia.csv", row.names = FALSE)
dim(db_final)
```

**Project Age column plot from database data:**

```{r eval = TRUE, echo = FALSE}
boxplot(db_final$Age, main = "Age of database data", xlab = "age", col = "khaki", border = "ivory4", horizontal = TRUE, notch = TRUE)
```